Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-01-10 ms.tex
wrote in results for A3 detector.
edits to discussion of amplifier offsets and dark frames.

\subsection{Amplifier Boundary Discontinuities}
\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
\caption{An example slope image from the LW OTIS Stability test.
No reference pixel correction is applied, leaving offsets at the amplifier boundaries.}\label{fig:ampOffsetsOtisGrismSlope}
\end{figure}

@@

For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^8$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm.

In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
If uncorrected, this extra read noise will contribution 7000 ppm to the time series (per frame)!
As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
We find the median of the entire image long the fast read (X) direction and subtract this from every row.
In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.

>>>>

\subsection{Amplifier Boundary Discontinuities}
\begin{figure}[!hbtp]
\centering
\includegraphics[width=.99\columnwidth]{amplifier_offsets_in_otis_lw_grism.pdf}
\caption{An example slope image from the LW OTIS Stability test.
{\it Top Panel:} No reference pixel correction is applied, leaving offsets at the amplifier boundaries.
{\it Middle Panel:} Reference pixel correction significantly reduces offsets between ampifiers.
{\it Bottom Panel:} The integrated flux (without background subtraction) shows substantially offsets in flux that are eliminated by reference pixel correction.
}\label{fig:ampOffsetsOtisGrismSlope}
\end{figure}

@@

For a read pair subtraction, the ``CDS'' (correlated double sample) read noise is 13.3 e$^-$ or 7.2 DN for the A5 detector studied here.
If we assume each pixel's read noise is uncorrelated with its neighbors, the total noise within the source aperture is then $\sqrt{N_{px}}$ where $N_{px}$ is the number of pixels and $RN$ is the read noise of a single pixel.
If we also assume that the background pixels are uncorrelated with each other and the source pixels, then the total noise in background-subtracted photometry is 1309 DN.
As an order of magnitude estimate for photometric stability, this read noise should be compared with the 3$\times 10^{6}$ DN/s (or 3$\times 10^7$ DN for a single full frame) in our CV3 detector stability test, so the read noise is expected to contribute $\sim$ 34 ppm per frame.
When averaging together $\sim$ 100 full frames over $\sim$ 60 minutes, this would only contribute 3 ppm to the transit depth uncertainty.

In our experimental time series, however, the standard deviation in the time series is 22,000 DN.
If uncorrected, this extra read noise will contribution 700 ppm to the time series (per frame)!
As can be seen in Figure \ref{fig:longDarkPhot}, there are significant correlations along the fast read (X) direction of the detector due to 1/f noise.
These can be reduced with the side reference pixels, which are designed to track electronic noise without the presence of background photon noise.
As can be seen in Figure \ref{fig:longDarkPhot} there are still additional correlations along the fast read direction, so we perform another correction step:
We find the median of the entire image long the fast read (X) direction and subtract this from every row.
In the latter case, the standard deviation of the time series drops to 6000 DN, but is still larger than the expectation of 1310 DN.

The A3 detector used for weak lens photometry has reduced 1/f noise.
The standard deviation of the raw time series is 15,000 compared with the 22,000 from the A5 (ALONG) detector.
